\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

%\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*] \renewcommand\labelitemi{$\circ$}}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
%\newcommand{\resumeItemListStart}{\begin{itemize}}
%\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://valaitis.net/}{\Large dr. Vytautas Valaitis}} & \href{mailto:vytautas@valaitis.net}{vytautas@valaitis.net}\\
  & +370 673 37482 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubItem{PhD in Informatics,}{Vilnius University, Lithuania, 2016.}
    \resumeSubItem{MSc in Informatics,}{Vilnius University, Lithuania, 2011.}
    \resumeSubItem{BSc in Software Engineering,}{Vilnius University, Lithuania, 2009.}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubItem{Vilnius University, Software Engineering Faculty,}{Assistant Professor, 2017 - Present.}
    \resumeSubItem{Monet Lt, UAB, Vilnius, Lithuania,}{Researcher, Lead Developer, 2018 - Present.}
    \resumeSubItem{Space Science and Technology Institute, Vilnius, Lithuania,}{Junior Researcher, 2018 - 2019.}
    \resumeSubItem{Vilnius University, Software Engineering Faculty,}{Lecturer, 2011 - 2017.}
    \resumeSubItem{Magma Solutions UAB, Vilnius, Lithuania,}{Engineer Developer, 2017.}
    \resumeSubItem{Vilnius University, Informatics Faculty,}{Junior Researcher, 2013 - 2015.}
    \resumeSubItem{VsI Inovatyvus inzineriniai projektai, Vilnius, Lithuania,}{Lead Developer, 2014 - 2015.}
    \resumeSubItem{UAB Teltonika, Vilnius, Lithuania,}{Embedded Developer, 2009 - 2011.}
    \resumeSubItem{AB Lietuvos Energija, Vilnius, Lithuania,}{Developer, 2007 - 2008.}
    \resumeSubItem{UAB Prototechnikos Iranga, Vilnius, Lithuania,}{Developer, 2006 - 2007.}
  \resumeSubHeadingListEnd

%-----------LANGUAGES-----------------
\section{Languages}
  \resumeSubHeadingListStart
    \resumeSubItem{Lithuanian,}{native}
    \resumeSubItem{English,}{good understanding speaking and writing.}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Hybrid UAV Kolibris,}{KAM-01-08, 2016.}
    \resumeSubItem{High-dimensionality and small data size problems in classification of biomedical and financial data,}{MIP-13011, 2013 - 2015.}
    \resumeSubItem{Lituanica SAT-1,}{2012 - 2014.}
  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------------
\section{Publications}
    \resumeSubHeadingListStart
    \resumeSubItem{Valaitis, V. et al Minimizing Hexapod Robot Foot Deviations Using Multilayer Perceptron.}{International Journal of Advanced Robotic Systems. Vol. 12, 2015.}
    \resumeSubItem{Valaitis, V. et al Piezoelectric Force Sensors for Hexapod Transportation Platform.}{Transport: Special Issue on Smart and Sustainable Transport. Vol. 30, No. 3, 2015.}
    \resumeSubItem{Valaitis, V. et al A Price We Pay for Inexact Dimensionality Reduction.}{Bioinformatics and Biomedical Engineering. p. 289-300, 2015.}
    \resumeSubItem{Valaitis, V. Learning Inverse Kinematics Problem in Changing Task Environment.}{The 12th Scandinavian AI conference. Vol 257, p. 299-302, 2013.}
  \resumeSubHeadingListEnd

%-----------CONFERENCES-----------------
\section{Conferences}
  \resumeSubHeadingListStart
    \resumeSubItem{The 3rd IEEE Workshop  on Bio-Inspired Signal and Image Processing, Vilnius, Lithuania, 2014.}{Multi-agent Neural Network Approach on Inverse Kinematics Problem in Changing Task Environment.}
    \resumeSubItem{The 12th Scandinavian AI conference, Aalborg, Denmark, 2013.}{Learning Inverse Kinematics Problem in Changing Task Environment.}
    \resumeSubItem{Numerical Computations: Theory and Algorithms, Falerna, Italy, 2013.}{Learning Motion Patterns of Robotic Arm.}
  \resumeSubHeadingListEnd

\end{document}
